\include{resume-include}
\usepackage[english]{babel}

\begin{document}
\pagestyle{empty}

\header{\vspace{-0.31cm}
		\highlight{contact}\\
		363 \textsc{Bis Rue des Pyrénées} \\
		75020 \textsc{Paris FRANCE}\\\vspace{0.4cm}
		+33 (0) 6 19 65 05 14\\
		etn@etnbrd.com\\
	}
	{%
		\textbf{\textsc{Etienne}\\
			      \textsc{Brodu}}\\\vspace{0.2cm}
			      @\highlight{etnbrd}
	}
	{%
		\textsc{PhD}\\
		\textsc{Software developer}\\
		\textsc{UI/UX Designer}
	}

\section{Publications}

	\subsection{Practical Aspects of High-Level Parallel Programming\\SAC '16}{
		Etienne Brodu, Stéphane Frénot, and Frédéric Oblé. 2016.\\
		Transforming JavaScript event-loop into a pipeline.\\
		In Proceedings of the 31st Annual ACM Symposium on Applied Computing (SAC '16).
		ACM, New York, NY, USA, 1906-1911.\\
		\href{http://dx.doi.org/10.1145/2851613.2851745}{DOI=10.1145/2851613.2851745}
	}

	\subsection{AWeS Workshop\\EuroSys '15}{
		Etienne Brodu, Stéphane Frénot, and Frédéric Oblé. 2015.\\
		Toward automatic update from callbacks to promises.\\
		In Proceedings of the 1st Workshop on All-Web Real-Time Systems (AWeS '15 – EuroSys Workshop).
		ACM, New York, NY, USA, Article 1, 8 pages.\\
		\href{http://doi.acm.org/10.1145/2749215.2749216}{DOI=10.1145/2749215.2749216}
	}

	\subsection{Posters and Demos\\Middleware '14}{
		Etienne Brodu, Stéphane Frénot, Fabien Cellier, and Frédéric Oblé. 2014.
		A compiler providing incremental scalability for web applications.\\
		In Proceedings of the Posters \& Demos Session (Middleware Posters and Demos '14).
		ACM, New York, NY, USA, 35-36.\\
		\href{http://doi.acm.org/10.1145/2678508.2678526}{DOI=10.1145/2678508.2678526}
	}

\section{Work Experiences}

	\subsection{Mars 2016 - February 2017}
		{CTO at WhatWeFund}

	\subsection{February 2013 - 2016}
		{PhD at Ècole Doctorale InfoMaths at the company Worldline. Liquid IT : Toward a better compromise between development scalability and performance scalability}

	\subsection{October - December 2012}
		{3 months contract as a Web developer / designer at Winterwell Associates, Edinburgh, Scotland. A team of experts in mathematics, statistics, computer science and artificial intelligence.}

	\subsection{April - September 2012}
		{Fifth year Internship: At Atos Worldline - Prospective and Emerging Projects, design contribution to a few projects \& Web development. Used HTML5 \& CSS 3, NodeJs, JavaScript.}

	\subsection{May - August 2011}
		{Fourth year Internship: At Philips HC, Eindhoven, Netherlands. Improvement of a collision avoidance system in an embedded medical system. Used C++ and intel VTune.}

	% \subsection{June - August 2010}
	% 	{Third year Internship: In the CITI laboratory (INRIA), working on android’s virtual machine dalvik to adapt to an OSGi modification. Used Java and C/C++ with JNI.}

\section{Education}
	\subsection{2013 - 2016}
		{PhD at Ècole Doctorale InfoMaths, Univérsité Lyon 1, French Institute for Research in Computer Science and Automation (INRIA), National Institute of Applied Sciences(INSA) of Lyon, France, funded by the company Worldline}

  \subsection{First semester 2011 - 2012}
  	{Master of Interaction Design \& Technologies. Chalmers University of Technology, Gothenburg, Sweden}

	\subsection{2007 - 2012}
		{Master of Engineering in Computer Sciences and Information Technology, National Institute of Applied Sciences (INSA) of Lyon, France}

\eject

\section{Special Skills}
	\subsection{Programming languages}
		{Javascript - Node.js, Go, Python, C/C++}

	\subsection{Web}
		{Javascript, HTML5 \& CSS3}

	\subsection{Tools \& Library}
	  {Git, zsh, \LaTeX, R}

	\subsection{Graphic Design}
		{Adobe Photoshop, Illustrator, Premiere, After Effects}

	\subsection{Languages}
		{French (native),\\English (fluent)}

\section{Miscellaneous}
	\subsection{Travel}
		{In Scotland, Sweden, Netherlands, Scandinavia, Germany, England, Ireland, Baltic States, Italia. Many experiences of live in a commune during those travels}

	\subsection{Associations activities}
		{BdE de l'Insa de Lyon (Student Union), free student-organized festival "\textit{les 24h de l'Insa de Lyon}" ...)}

	\subsection{Activities}
		{Camp counselor (BAFA + PSC1)}

	\subsection{Sport}
		{Savate (french boxing), climbing, snowboarding, running ...}
\end{document}
